\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-29 paper.qmd
Add citations

The default number of bins $b=b_1\times b_2$ is computed based on the sample size, by setting $b_1=n^{1/3}$, consistent with the Diaconis-Freedman rule @REF-doi:10.1007/BF01025868. The value of $b_2$ is determined analytically by $b_1, q, r_2$. Values of $b_1$ between 2 and $b_1 = \frac{n}{2}$ are allowed. FIG XXX(b) shows the effect of different choices of $b_1$ on the MSE of the fitted model. XXX Are you showing $b_1$ or $b$ here????

>>>>

The default number of bins $b=b_1\times b_2$ is computed based on the sample size, by setting $b_1=n^{1/3}$, consistent with the Diaconis-Freedman rule [@freedman1981]. The value of $b_2$ is determined analytically by $b_1, q, r_2$. Values of $b_1$ between $2$ and $b_1 = \frac{n}{2}$ are allowed. FIG XXX(b) shows the effect of different choices of $b_1$ on the MSE of the fitted model. XXX Are you showing $b_1$ or $b$ here???? $b$

### 2024-07-29 paper.tex
Add citations

The default number of bins \(b=b_1\times b_2\) is computed based on the
sample size, by setting \(b_1=n^{1/3}\), consistent with the
Diaconis-Freedman rule \citet{REF-doi:10.1007/BF01025868}. The value of
\(b_2\) is determined analytically by \(b_1, q, r_2\). Values of \(b_1\)
between 2 and \(b_1 = \frac{n}{2}\) are allowed. FIG XXX(b) shows the
effect of different choices of \(b_1\) on the MSE of the fitted model.
XXX Are you showing \(b_1\) or \(b\) here????

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/mnist_model_2d.png}

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/img_error_sample_within.png}

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/img_error_sample_out.png}

>>>>

The default number of bins \(b=b_1\times b_2\) is computed based on the
sample size, by setting \(b_1=n^{1/3}\), consistent with the
Diaconis-Freedman rule \citep{freedman1981}. The value of \(b_2\) is
determined analytically by \(b_1, q, r_2\). Values of \(b_1\) between
\(2\) and \(b_1 = \frac{n}{2}\) are allowed. FIG XXX(b) shows the effect
of different choices of \(b_1\) on the MSE of the fitted model. XXX Are
you showing \(b_1\) or \(b\) here???? \(b\)

@@

\includegraphics{figures/mnist/mnist_model_2d.png}

@@

\includegraphics{figures/mnist/img_error_sample_within.png}

@@

\includegraphics{figures/mnist/img_error_sample_out.png}
